Alex's Notes and Text Fragments for the JSS Manuscript

### 2023-08-11 paper/article.Rmd
wording

The model assessment is now repeated again using spatial CV resampling, for which the only required change is to replace `"repeated_cv"` by `"repeated_spcv_coords"`.

>>>>

The model assessment is now repeated again using spatial CV resampling, for which the only required change is to replace `"repeated_cv"` with `"repeated_spcv_coords"`.
